Analysis of the implications of the ``Moral Machine'' project as an implementation of the concept of ``coherent, extrapolated volition'' for building clustered trust in autonomous machines

### 2023-03-09 ART_Noh/Noh.tex
Editorial corrections added
Additional corrections added

\begin{artengenv}{Hyungrae Noh}
	{Shannon-inspired information in the clinical use of neural signals concerning post-comatose patients}
	{Shannon-inspired information in the clinical use of neural signals\ldots}
	{Shannon-inspired information in the clinical use of neural signals\\concerning post-comatose patients}
	{Sunchon National Unviersity}
	{Post-comatose patients are classified as being in a~minimally conscious state when they have executive functions. Because traditional behavioral assessments may not capture signs of executive functions in post-comatose patients, clinicians look to localized brain activities in response to task instructions, such as imagining wiggling toes, to diagnose minimal consciousness. This paper critically assesses the assumption underlying such alternative methods: that brain activities are neural signals conveying information about minimal consciousness. Based on a~Shannon-inspired idea of information, I~distinguish between informational and engineering aspects of clinical tasks. The informational aspect concerns the conditional probability that, for example, given activity in the motor areas of the brain in response to task instructions, a~patient is imagining wiggling toes. The engineering aspect concerns efficient activation of the relevant brain areas in a~patient under the task conditions. This distinction shows that the current alternative methods are not informationally problematic, but are structurally ``ill-formed.'' For instance, the toe-imagery task requires the capacity to comprehend syntactically complex sentences, which can be dissociated from minimal consciousness. I~propose a~misrepresentation task, which tests the capacity to misconceptualize lukewarm water as melting wax, as a~supplement to the current alternative methods. This task is as informationally reliable as these methods, but is structurally ``well-formed,'' as it does not rely methodologically on prerequisites such as language comprehension.
	}
	{post-comatose disorders of consciousness, Shannon's theory of information, minimal consciousness, mental action.}

\section{Introduction}
\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{M}{}inimally conscious post-comatose patients (henceforth, MCP patients) can have limited executive functions that allow for the patients to follow simple instructions or respond to certain stimulations. Signs of residual executive functions provide clinicians with strong evidence of eventual recovery of consciousness
%\label{ref:RNDc52VR2C0H1}(Naccache, 2018; Rohaut, Eliseyev and Claassen, 2019).
\parencites[][]{naccache_minimally_2018}[][]{rohaut_uncovering_2019}. %
 Thus, delayed recognition of such signs may lead to suboptimal clinical care 
%\label{ref:RND36iYhUl47e}(van Erp et al., 2019),
\parencite[van][]{van_erp_unexpected_2019}, %
 distorted prognostic figures for rehabilitation 
%\label{ref:RNDDiumYQqtvx}(Ansell, 1993),
\parencite[][]{ansell_slow--recover_1993}, %
 or ethical problems 
%\label{ref:RNDY4B7wdnTLX}(Peterson and Bayne, 2018; Noh, 2022).
\parencites[][]{peterson_post-comatose_2018}[][]{noh_behavioral_2022}. %
 Such signs, however, might not be captured by traditional behavioral assessments (e.g., eye tracking, speaking, etc.) because limited executive functions can be dissociated from the capacity to perform overt behaviors 
%\label{ref:RND1VSfdAw16s}(Teasdale and Jennett, 1974; Andrews et al., 1996).
\parencites[][]{teasdale_assessment_1974}[][]{andrews_misdiagnosis_1996}. %
 Although some traditional behavioral assessment methods can improve diagnostic accuracy 
%\label{ref:RNDkWoQFW7Rb7}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 differentiating MCP patients from patients in a~vegetative state remains challenging 
%\label{ref:RNDXmlWJMWjeY}(van Erp et al., 2015).
\parencite[van][]{van_erp_vegetative_2015}.%

@@

Mutual information between the brain event, $S$, and a~set of mental events, $M$, is:
$$I(S:M)=H(M)H(MS).\footnote{The idea of analyzing the informational aspect of active paradigm tasks originates from Noh
%\label{ref:RNDjBvUliVaOb}(2018, pp.181–185).
\parencite*[][pp.181–185]{noh_no-report_2018}.%
}$$
\textit{H} refers to Shannon entropy. To compare $M_1$ and $M_2$, however, individual events need to be considered rather than the average. Because the toe-imagery task depends on the assumption that the detection of $S$ particularly reduces the uncertainty of the mental event that subjects are imagining wiggling toes, let's take $M_1$ as referring to this mental event. The amount of uncertainty of $M_1$ that $S$ reduces is:
$$I(S:M_1)=I(M_1)I(M_1S)\log _2P(M_1)\log _2P(M_1S)\log _2\frac{P(M_1S)}{P(M_1)}.$$
As $\log _2\frac{P(M_1S)}{P(M_1)}$ gets more and more positive, $S$ will represent greater accuracy about $M_1$. If $\log _2\frac{P(M_1S}{P(M_1)}$ is greater than $\log _2\frac{P(M_2S)}{P(M_2)}$, then the observation of $S$ provides clinicians with evidence that patients in the toe-imagery task who show activities in the medial premotor cortex are minimally conscious. If the latter is greater than, or equivalent to, the former, then $S$ alone cannot provide that evidence.

To estimate the value of $\log _2\frac{P(M_1S)}{P(M_1)}$, we need to understand the background conditions of the toe-imagery task. Notice that the patients in Cruse et al.'s
%\label{ref:RND2y1XLkJnMb}(2011)
\parencite*[][]{cruse_bedside_2011} %
 experiment were initially diagnosed with the vegetative state by traditional behavioral assessments. Given that the misdiagnosis rate of traditional behavioral assessments is 41\% 
%\label{ref:RNDQvnJPYKu8r}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 the unconditional probability that Cruse et al.'s patients were conscious, i.e., $P(M_1)$, is lower than the unconditional probability that they were in the vegetative state, i.e., $P(M_2)$. So, $\log _2\frac{P(M_1S}{P(M_1)}$ is greater than $\log _2\frac{P(M_2S)}{P(M_2)}$ if $P(M_1 | S)$ is greater than, or equivalent to, $P(M_2 | S)$.

$P(M_1 | S)$ can be accounted for by the reversed strong correlation that holds between activities in motor areas and the corresponding mental-motor action. According to relevant experiments
%\label{ref:RND3XvevSKtpr}(e.g. Pfurtscheller and Neuper, 1997; Ehrsson, Geyer and Naito, 2003)
\parencites[e.g.,][]{pfurtscheller_motor_1997}[][]{ehrsson_imagery_2003} %
 in which healthy subjects were instructed to mentally act (e.g., they were instructed to imagine raising their left arms without making any actual motor movement), activities in the relevant motor areas were observed in the majority of the subjects. Provided that $P$ (activities in the relevant motor areas{\textbar}mental-motor action) is high, it seems that $P(M_1 | S)$ is relatively high as well.

@@

Nonetheless, no such explanation is available. Consider a~semantic priming effect, which refers to cases where automated activities in the somatotopy of the motor and premotor cortex are observed for a~few milliseconds when a~subject hears an action-word such as ``kick''
%\label{ref:RNDtVfb2YZ1ak}(Pulvermüller, 2005).
\parencite[][]{pulvermuller_brain_2005}. %
 Now, consider $M_2$ as a~toe-related nonconscious mental event grounded by a~semantic priming effect. $P(M_2 | S)$ in this sense, however, is very low for two reasons. First, the semantic priming effect has been observed when a~single word is given, but not when a~whole sentence, such as ``Imagine wiggling all of your toes,'' is given 
%\label{ref:RND5xoKfn4zNx}(Raposo et al., 2009).
\parencite[][]{raposo_modulation_2009}. %
 Second, the effect lasts for a~very short time, but the activity in Cruse et al.'s experiment persisted for more than a~few seconds. Because there is no alternative explanation, $\log _2\frac{P(M_1S}{P(M_1)}$ is greater than $\log _2\frac{P(M_2S)}{P(M_2)}$.

@@

Recall that in Cruse et al.'s
%\label{ref:RND5hclfQLLkX}(2011)
\parencite*[][]{cruse_bedside_2011} %
 toe-imagery task, a~strong correlation between activities in motor areas and the corresponding mental-motor action holds because $P(M_1 | S)$ is relatively greater than $P(M_2 | S)$.\footnote{Notice that $P(M_2)$ is always greater than $P(M_1)$ in both active and passive paradigms because every MCP patient in the experiments was initially diagnosed with the vegetative state by traditional behavioral assessments. Specifically, because the misdiagnosis rate of traditional behavior assessments is 41\%, $P(M_2)$ is roughly 60\%.} So, we should compare $P$ (the subject is minimally conscious{\textbar}the P300b response) and $P$ (the subject is nonconscious{\textbar}the P300b response). According to the relevant studies, the P300b response requires working memory. Specifically, the P300b response is accounted for by the following hypotheses: Noticing global oddballs requires working memory and predictive coding 
%\label{ref:RNDXe3oyEzvUf}(Garrido et al., 2008; 2009);
\parencites[][]{garrido_functional_2008}[][]{garrido_repetition_2009}; %
 the P300b response is a~neural signature of postperceptual processing, such as working memory 
%\label{ref:RNDD9OoRT2KMc}(Cohen et al., 2020);
\parencite[][]{cohen_distinguishing_2020}; %
 and the P300b response is a~neural signature of working memory–guided categorization processes 
%\label{ref:RND1OFfKua7Q6}(Rac-Lubashevsky and Kessler, 2019).
\parencite[][]{rac-lubashevsky_revisiting_2019}. %
 If there is no alternative explanation of the P300b response, and if working memory is a~sign of minimal consciousness 
%\label{ref:RNDkNGafGH8qa}(Ansell, 1993; Bekinschtein et al., 2009; King et al., 2013),
\parencites[][]{ansell_slow--recover_1993}[][]{bekinschtein_neural_2009}[][]{king_single-trial_2013}, %
 then $P$(the subject is minimally conscious{\textbar}the P300b response) is greater than $P$ (the subject is nonconscious{\textbar}the P300b response).

@@

In order to analyze the engineering aspect of the toe-imagery task, we must first distinguish between types of mental action. An essential component of mental-motor action is that a~subject mentally executes an instructed mental-motor action from the first-person perspective
%\label{ref:RND1pm2quQW6r}(i.e. kinesthetic mental-motor action Ehrsson, Geyer and Naito, 2003).
\parencite[i.e., kinesthetic mental-motor action][]{ehrsson_imagery_2003}. %
 Alternatively, subjects can imagine seeing themselves or another person performing an action from an external view (i.e., visual motor imagery), which may be primarily visual in character rather than involving kinesthetic characteristics 
%\label{ref:RNDNPkyueF1mq}(Sekiyama, 1983).
\parencite[][]{sekiyama_mental_1983}. %
 According to Annett 
%\label{ref:RND1637syDSd3}(1995),
\parencite*[][]{annett_motor_1995}, %
 without specific instructions to perform a~kinesthetic mental-motor action, such that when the instruction ``Imagine wiggling toes'' is given, subjects may either perform a~kinesthetic mental-motor action or conceive visual motor imagery. Kinesthetic mental-motor action correlates significantly more strongly with activities in the relevant motor areas than does visual motor imagery, implying that visual motor imagery might not activate the relevant motor areas 
%\label{ref:RNDUsbP29uqd5}(Neuper et al., 2005).
\parencite[][]{neuper_imagery_2005}. %
 Hence, Cruse et al.'s toe-imagery task should have been designed in such a~way that behaviorally nonresponsive MCP patients are clearly instructed to perform a~kinesthetic mental-motor action and that they can clearly comprehend the instruction.

@@

In order to analyze the informational aspect of the misrepresentation task, a~distinction between two types of placebo/nocebo responses needs to be discussed. Benedetti et al.
%\label{ref:RNDdlH5q4SDXG}(2003)
\parencite*[][]{benedetti_conscious_2003} %
 distinguish between placebo/nocebo responses by conditioning and expectation, where the former concerns unconscious processes such as hormone secretion and the latter concerns conscious processes such as pain or motor performance. The misrepresentation task does not involve conditioning: it does not expose a~subject to repeated stimulus-behavioral patterns, nor does it reward/punish the subject for behaving in a~particular way in response to certain stimulations. Rather, the misrepresentation task tests whether a~subject can form an expectation of the forthcoming ``noxious'' stimulus. According to Colloca and Benedetti 
%\label{ref:RND0I6Gy29YP0}(2009),
\parencite*[][]{colloca_placebo_2009}, %
 observational social learning produces placebo/nocebo responses by expectation. The purported brain activity in the misrepresentation task is a~mark of a~nocebo response due to expectation produced by social learning (i.e., the instructor displays a~painful facial expression when the tactile stimulus is paired with melting wax). Most importantly, placebo/nocebo responses by expectation generally require executive functions 
%\label{ref:RND0aFSOWMyRk}(Benedetti, Carlino and Pollo, 2011, p.239).
\parencite[][p.239]{benedetti_how_2011}. %
 Thus, if localized activities in prefrontal areas are observed in the melting-wax task but not in the control task, then the best explanation for the activities is the one that appeals to minimal consciousness. In a~nutshell, the misrepresentation task is informationally reliable because $P$ (nocebo effect by expectation{\textbar}activities in prefrontal areas) is greater than $P$ (nocebo effect by conditioning{\textbar}activities in prefrontal areas).

>>>>

\begin{artengenv}{Hyungrae Noh}
	{Shannon-inspired information in the clinical use of neural signals concerning post-comatose patients}
	{Shannon-inspired information in the clinical use of neural signals\ldots}
	{Shannon-inspired information in the clinical use of neural signals\\concerning post-comatose patients}
	{Sunchon National University, South Korea}
	{Post-comatose patients are classified as being in a~minimally conscious state when they have executive functions. Because traditional behavioral assessments may not capture signs of executive functions in post-comatose patients, clinicians look to localized brain activities in response to task instructions, such as imagining wiggling toes, to diagnose minimal consciousness. This paper critically assesses the assumption underlying such alternative methods: that brain activities are neural signals conveying information about minimal consciousness. Based on a~Shannon-inspired idea of information, I~distinguish between informational and engineering aspects of clinical tasks. The informational aspect concerns the conditional probability that, for example, given activity in the motor areas of the brain in response to task instructions, a~patient is imagining wiggling toes. The engineering aspect concerns efficient activation of the relevant brain areas in a~patient under the task conditions. This distinction shows that the current alternative methods are not informationally problematic, but are structurally ``ill-formed.'' For instance, the toe-imagery task requires the capacity to comprehend syntactically complex sentences, which can be dissociated from minimal consciousness. I~propose a~misrepresentation task, which tests the capacity to misconceptualize lukewarm water as melting wax, as a~supplement to the current alternative methods. This task is as informationally reliable as these methods, but is structurally ``well-formed,'' as it does not rely methodologically on prerequisites such as language comprehension.
	}
	{post-comatose disorders of consciousness, Shannon's theory of information, minimal consciousness, mental action.}

\section{Introduction}
\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{M}{}inimally conscious post-comatose patients (henceforth, MCP patients) can have limited executive functions that allow for the patients to follow simple instructions or respond to certain stimulations. Signs of residual executive functions provide clinicians with strong evidence of eventual recovery of consciousness
%\label{ref:RNDc52VR2C0H1}(Naccache, 2018; Rohaut, Eliseyev and Claassen, 2019).
\parencites[][]{naccache_minimally_2018}[][]{rohaut_uncovering_2019}. %
 Thus, delayed recognition of such signs may lead to suboptimal clinical care 
%\label{ref:RND36iYhUl47e}(van Erp et al., 2019),
\parencite[][]{van_erp_unexpected_2019}, %
 distorted prognostic figures for rehabilitation 
%\label{ref:RNDDiumYQqtvx}(Ansell, 1993),
\parencite[][]{ansell_slow--recover_1993}, %
 or ethical problems 
%\label{ref:RNDY4B7wdnTLX}(Peterson and Bayne, 2018; Noh, 2022).
\parencites[][]{peterson_post-comatose_2018}[][]{noh_behavioral_2022}. %
 Such signs, however, might not be captured by traditional behavioral assessments (e.g., eye tracking, speaking, etc.) because limited executive functions can be dissociated from the capacity to perform overt behaviors 
%\label{ref:RND1VSfdAw16s}(Teasdale and Jennett, 1974; Andrews et al., 1996).
\parencites[][]{teasdale_assessment_1974}[][]{andrews_misdiagnosis_1996}. %
 Although some traditional behavioral assessment methods can improve diagnostic accuracy 
%\label{ref:RNDkWoQFW7Rb7}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 differentiating MCP patients from patients in a~vegetative state remains challenging 
%\label{ref:RNDXmlWJMWjeY}(van Erp et al., 2015).
\parencite[][]{van_erp_vegetative_2015}.%

@@

Mutual information between the brain event, $S$, and a~set of mental events, $M$, is:
$$I(S:M)=H(M)-H(M|S).\footnote{The idea of analyzing the informational aspect of active paradigm tasks originates from Noh
%\label{ref:RNDjBvUliVaOb}(2018, pp.181–185).
\parencite*[][pp.181–185]{noh_no-report_2018}.%
}$$
\textit{H} refers to Shannon entropy. To compare $M_1$ and $M_2$, however, individual events need to be considered rather than the average. Because the toe-imagery task depends on the assumption that the detection of $S$ particularly reduces the uncertainty of the mental event that subjects are imagining wiggling toes, let's take $M_1$ as referring to this mental event. The amount of uncertainty of $M_1$ that $S$ reduces is:
%$$I(S:M_1)=I(M_1)-I(M_1|S)=-\log _2P(M_1)+\log _2P(M_1|S)=\log _2\frac{P(M_1|S)}{P(M_1)}.$$
\begin{equation*}
\begin{split}
I(S:M_1)&=I(M_1)-I(M_1|S)\\
&=-\log _2P(M_1)+\log _2P(M_1|S)\\
&=\log _2\frac{P(M_1|S)}{P(M_1)}.
\end{split}
\end{equation*}
As $\log _2\frac{P(M_1|S)}{P(M_1)}$ gets more and more positive, $S$ will represent greater accuracy about $M_1$. If $\log _2\frac{P(M_1|S)}{P(M_1)}$ is greater than $\log _2\frac{P(M_2|S)}{P(M_2)}$, then the observation of $S$ provides clinicians with evidence that patients in the toe-imagery task who show activities in the medial premotor cortex are minimally conscious. If the latter is greater than, or equivalent to, the former, then $S$ alone cannot provide that evidence.

To estimate the value of $\log _2\frac{P(M_1|S)}{P(M_1)}$, we need to understand the background conditions of the toe-imagery task. Notice that the patients in Cruse et al.'s
%\label{ref:RND2y1XLkJnMb}(2011)
\parencite*[][]{cruse_bedside_2011} %
 experiment were initially diagnosed with the vegetative state by traditional behavioral assessments. Given that the misdiagnosis rate of traditional behavioral assessments is 41\% 
%\label{ref:RNDQvnJPYKu8r}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 the unconditional probability that Cruse et al.'s patients were conscious, i.e., $P(M_1)$, is lower than the unconditional probability that they were in the vegetative state, i.e., $P(M_2)$. So, $\log _2\frac{P(M_1|S)}{P(M_1)}$ is greater than $\log _2\frac{P(M_2|S)}{P(M_2)}$ if $P(M_1 | S)$ is greater than, or equivalent to, $P(M_2 | S)$.

$P(M_1 | S)$ can be accounted for by the reversed strong correlation that holds between activities in motor areas and the corresponding mental-motor action. According to relevant experiments
%\label{ref:RND3XvevSKtpr}(e.g. Pfurtscheller and Neuper, 1997; Ehrsson, Geyer and Naito, 2003)
\parencites[e.g.,][]{pfurtscheller_motor_1997}[][]{ehrsson_imagery_2003} %
 in which healthy subjects were instructed to mentally act (e.g., they were instructed to imagine raising their left arms without making any actual motor movement), activities in the relevant motor areas were observed in the majority of the subjects. Provided that $P$(activities in the relevant motor areas{\textbar}mental-motor action) is high, it seems that $P(M_1 | S)$ is relatively high as well.

@@

Nonetheless, no such explanation is available. Consider a~semantic priming effect, which refers to cases where automated activities in the somatotopy of the motor and premotor cortex are observed for a~few milliseconds when a~subject hears an action-word such as ``kick''
%\label{ref:RNDtVfb2YZ1ak}(Pulvermüller, 2005).
\parencite[][]{pulvermuller_brain_2005}. %
 Now, consider $M_2$ as a~toe-related nonconscious mental event grounded by a~semantic priming effect. $P(M_2 | S)$ in this sense, however, is very low for two reasons. First, the semantic priming effect has been observed when a~single word is given, but not when a~whole sentence, such as ``Imagine wiggling all of your toes,'' is given 
%\label{ref:RND5xoKfn4zNx}(Raposo et al., 2009).
\parencite[][]{raposo_modulation_2009}. %
 Second, the effect lasts for a~very short time, but the activity in Cruse et al.'s experiment persisted for more than a~few seconds. Because there is no alternative explanation, $\log _2\frac{P(M_1|S)}{P(M_1)}$ is greater than $\log _2\frac{P(M_2|S)}{P(M_2)}$.

@@

Recall that in Cruse et al.'s
%\label{ref:RND5hclfQLLkX}(2011)
\parencite*[][]{cruse_bedside_2011} %
 toe-imagery task, a~strong correlation between activities in motor areas and the corresponding mental-motor action holds because $P(M_1 | S)$ is relatively greater than $P(M_2 | S)$.\footnote{Notice that $P(M_2)$ is always greater than $P(M_1)$ in both active and passive paradigms because every MCP patient in the experiments was initially diagnosed with the vegetative state by traditional behavioral assessments. Specifically, because the misdiagnosis rate of traditional behavior assessments is 41\%, $P(M_2)$ is roughly 60\%.} So, we should compare $P$(the subject is minimally conscious{\textbar}the P300b response) and $P$(the subject is nonconscious{\textbar}the P300b response). According to the relevant studies, the P300b response requires working memory. Specifically, the P300b response is accounted for by the following hypotheses: Noticing global oddballs requires working memory and predictive coding 
%\label{ref:RNDXe3oyEzvUf}(Garrido et al., 2008; 2009);
\parencites[][]{garrido_functional_2008}[][]{garrido_repetition_2009}; %
 the P300b response is a~neural signature of postperceptual processing, such as working memory 
%\label{ref:RNDD9OoRT2KMc}(Cohen et al., 2020);
\parencite[][]{cohen_distinguishing_2020}; %
 and the P300b response is a~neural signature of working memory–guided categorization processes 
%\label{ref:RND1OFfKua7Q6}(Rac-Lubashevsky and Kessler, 2019).
\parencite[][]{rac-lubashevsky_revisiting_2019}. %
 If there is no alternative explanation of the P300b response, and if working memory is a~sign of minimal consciousness 
%\label{ref:RNDkNGafGH8qa}(Ansell, 1993; Bekinschtein et al., 2009; King et al., 2013),
\parencites[][]{ansell_slow--recover_1993}[][]{bekinschtein_neural_2009}[][]{king_single-trial_2013}, %
 then $P$(the subject is minimally conscious{\textbar}the P300b response) is greater than $P$(the subject is nonconscious{\textbar}the P300b response).

@@

In order to analyze the engineering aspect of the toe-imagery task, we must first distinguish between types of mental action. An essential component of mental-motor action is that a~subject mentally executes an instructed mental-motor action from the first-person perspective
%\label{ref:RND1pm2quQW6r}(i.e. kinesthetic mental-motor action Ehrsson, Geyer and Naito, 2003).
\parencite[i.e., kinesthetic mental-motor action;][]{ehrsson_imagery_2003}. %
 Alternatively, subjects can imagine seeing themselves or another person performing an action from an external view (i.e., visual motor imagery), which may be primarily visual in character rather than involving kinesthetic characteristics 
%\label{ref:RNDNPkyueF1mq}(Sekiyama, 1983).
\parencite[][]{sekiyama_mental_1983}. %
 According to Annett 
%\label{ref:RND1637syDSd3}(1995),
\parencite*[][]{annett_motor_1995}, %
 without specific instructions to perform a~kinesthetic mental-motor action, such that when the instruction ``Imagine wiggling toes'' is given, subjects may either perform a~kinesthetic mental-motor action or conceive visual motor imagery. Kinesthetic mental-motor action correlates significantly more strongly with activities in the relevant motor areas than does visual motor imagery, implying that visual motor imagery might not activate the relevant motor areas 
%\label{ref:RNDUsbP29uqd5}(Neuper et al., 2005).
\parencite[][]{neuper_imagery_2005}. %
 Hence, Cruse et al.'s toe-imagery task should have been designed in such a~way that behaviorally nonresponsive MCP patients are clearly instructed to perform a~kinesthetic mental-motor action and that they can clearly comprehend the instruction.

@@

In order to analyze the informational aspect of the misrepresentation task, a~distinction between two types of placebo/nocebo responses needs to be discussed. Benedetti et al.
%\label{ref:RNDdlH5q4SDXG}(2003)
\parencite*[][]{benedetti_conscious_2003} %
 distinguish between placebo/nocebo responses by conditioning and expectation, where the former concerns unconscious processes such as hormone secretion and the latter concerns conscious processes such as pain or motor performance. The misrepresentation task does not involve conditioning: it does not expose a~subject to repeated stimulus-behavioral patterns, nor does it reward/punish the subject for behaving in a~particular way in response to certain stimulations. Rather, the misrepresentation task tests whether a~subject can form an expectation of the forthcoming ``noxious'' stimulus. According to Colloca and Benedetti 
%\label{ref:RND0I6Gy29YP0}(2009),
\parencite*[][]{colloca_placebo_2009}, %
 observational social learning produces placebo/nocebo responses by expectation. The purported brain activity in the misrepresentation task is a~mark of a~nocebo response due to expectation produced by social learning (i.e., the instructor displays a~painful facial expression when the tactile stimulus is paired with melting wax). Most importantly, placebo/nocebo responses by expectation generally require executive functions 
%\label{ref:RND0aFSOWMyRk}(Benedetti, Carlino and Pollo, 2011, p.239).
\parencite[][p.239]{benedetti_how_2011}. %
 Thus, if localized activities in prefrontal areas are observed in the melting-wax task but not in the control task, then the best explanation for the activities is the one that appeals to minimal consciousness. In a~nutshell, the misrepresentation task is informationally reliable because $P$(nocebo effect by expectation{\textbar}activities in prefrontal areas) is greater than $P$(nocebo effect by conditioning{\textbar}activities in prefrontal areas).

### 2023-03-09 ART_Soloducha/Soloducha.tex
Additional corrections added

\begin{artengenv}{Krzysztof Sołoducha}
	{Analysis of the implications of the Moral Machine project as an implementation of the concept of coherent extrapolated volition for building clustered trust in autonomous machines}
	{Analysis of the implications of the Moral Machine project\ldots}
	{Analysis of the implications of the Moral Machine project as\\an implementation of the concept of coherent extrapolated volition\\for building clustered trust in autonomous machines}
	{Military University of Technology}
	{In this paper, we focus on the analysis of Eliezer Yudkowsky's concept of ``coherent extrapolated volition'' (CEV) as a~response to the need for a~post-conventional, persuasive morality that meets the criteria of active trust in the sense of Anthony Giddens, which could be used in the case of autonomous machines. Based on the analysis of the results of the Moral Machine project, we formulate some guidelines for transformation of the idea of a~coherent extrapolated volition into the concept of a~coherent, extrapolated and clustered volition. The argumentation used in the paper is intended to show that the idea of CEV transformed into its clustered version can be used to build a~technically and socially efficient decision-making pattern database for autonomous machines.
	}
	{ethics of artificial intelligence, ethics of autonomous machines, trust in artificial intelligence, moral machine project, coherent extrapolated volition.}

@@

The project developers attempted to test the importance of the nine preferences studied in the project. Figures developed in the project show the nine AMCE values extracted from the data of the Moral Machine project. In each row of figures, the bar shows the difference between the probability of saving the character with the attribute on the right and the probability of saving the character with the attribute on the left, compared to the spread of all other attributes.

@@

In Loop scenario we deal with the active sacrifice of one life for the sake of five. The act of decision itself, however, does not result in direct killing. Indirect killing is faced If the man in blue on the bridge pushes the person next to him, that person will fall on the track. The trolley will hit that person and therefore not kill the five people working there. In Footbridge scenario we deal with the active sacrifice of one life for the sake of five linked with the act of direct killing.

@@

In order to find answers to this question, we carried out a~sample survey on 34 students aged between 18 and 39, who were asked about their preferences in this respect. From a~methodological point of view, this is a~survey carried out in the form of an online survey. Its aim was to examine the basic preferences of possible users of autonomous machines in terms of the expected level of clustering. The survey has no ambition to be a~representative poll. Our objective is rather to identify certain trends in user preferences.
%Below you find most interesting results of the survey in terms of clustering of preferences of AV users.
\enlargethispage{2\baselineskip}
\begin{figure}[H]
 \begin{center}
 \includegraphics[width=.8\textwidth]{ART_Soloducha/illustration1.pdf}%
 \end{center}%
 \caption{Most interesting results of the survey in terms of clustering of preferences of AV users. Source: Author's study.}\label{sol-ill1}
\end{figure}
%Illustration 1

@@

The other problem investigated in the survey was the level of clustering. The top level used in the research was the continental one. The majority of respondents preferred the level of state. The level of clustering reflecting Ingelhart-Welzel's map of cultural influences used in the research mentioned above did not appear among the questions. This does not reflect traditional geographical and administrative distinctions.

@@

Secondly, such considerations can be conducted under the assumption that the best path to their implementation is to define cognitive processes (including those of a~moral nature) as consisting of information processing. What may help here may be the assumption that such a~definition of moral cognition would not be a~naturalisation
%\label{ref:RNDAVNr8uUo2k}(Rosenbloom, 2015).
\parencite[][]{peruzzi_beginners_2015}. %
 This also could help to eliminate the troubling issue of the \textit{is-ought problem}. Although it is an issue considered by some theorists to be an illusory 
%\label{ref:RNDke81GSJMB7}(Gellner, 2005)
\parencite[][]{gellner_words_2005} %
 and an argument that is treated as untenable nowadays 
%\label{ref:RNDv1WxbP4FgK}(Searle, 1964)
\parencite[][]{searle_how_1964} %
 from point of view of ``weak'' rationality—as mentioned above.

@@

\paragraph{Acknowledgments.}
The author wishes to thank anonymous helpful referees whose insightful comments helped improve the quality of the present paper. Most certainly, if there are still some errors remaining, they are my own responsibility.

>>>>

\begin{artengenv}{Krzysztof Sołoducha}
	{Analysis of the implications of the Moral Machine project as an implementation of the concept of coherent extrapolated volition for building clustered trust in autonomous machines}
	{Analysis of the implications of the Moral Machine project\ldots}
	{Analysis of the implications of the Moral Machine project as\\an implementation of the concept of coherent extrapolated volition\\for building clustered trust in autonomous machines}
	{Military University of Technology, Poland}
	{In this paper, we focus on the analysis of Eliezer Yudkowsky's concept of ``coherent extrapolated volition'' (CEV) as a~response to the need for a~post-conventional, persuasive morality that meets the criteria of active trust in the sense of Anthony Giddens, which could be used in the case of autonomous machines. Based on the analysis of the results of the Moral Machine project, we formulate some guidelines for transformation of the idea of a~coherent extrapolated volition into the concept of a~coherent, extrapolated and clustered volition. The argumentation used in the paper is intended to show that the idea of CEV transformed into its clustered version can be used to build a~technically and socially efficient decision-making pattern database for autonomous machines.
	}
	{ethics of artificial intelligence, ethics of autonomous machines, trust in artificial intelligence, moral machine project, coherent extrapolated volition.}

@@

%The project developers attempted to test the importance of the nine preferences studied in the project.
Figures developed in the project show the nine AMCE values extracted from the data of the Moral Machine project. In each row of figures, the bar shows the difference between the probability of saving the character with the attribute on the right and the probability of saving the character with the attribute on the left, compared to the spread of all other attributes.

@@

In Loop scenario we deal with the active sacrifice of one life for the sake of five. The act of decision itself, however, does not result in direct killing. Indirect killing is faced if the man in blue on the bridge pushes the person next to him, that person will fall on the track. The trolley will hit that person and therefore not kill the five people working there. In Footbridge scenario we deal with the active sacrifice of one life for the sake of five linked with the act of direct killing.

@@

In order to find answers to this question, we carried out a~sample survey on 34 students aged between 18 and 39, who were asked about their preferences in this respect. From a~methodological point of view, this is a~survey carried out in the form of an online questionnaire. Its aim was to examine the basic preferences of possible users of autonomous machines in terms of the expected level of clustering. The survey has no ambition to be a~representative poll. Our objective is rather to identify certain trends in user preferences.
%Below you find most interesting results of the survey in terms of clustering of preferences of AV users.
\enlargethispage{2\baselineskip}
\begin{figure}[H]
 \begin{center}
 \includegraphics[width=.8\textwidth]{ART_Soloducha/illustration1.pdf}%
 \end{center}%
 \caption{Most interesting results of the survey in terms of clustering of preferences of AV users. Source: Author's study.}\label{sol-ill1}
\end{figure}
%Illustration 1

@@

The other problem investigated in the survey was the level of clustering. The top level used in the research was the continental one. The majority of respondents preferred the level of state. The level of clustering reflecting Ingelhart-Welzel's map of cultural influences used in the research mentioned above did not appear among the questions. This does not reflect traditional geographical and administrative distinctions.
\enlargethispage{2\baselineskip}

@@

Secondly, such considerations can be conducted under the assumption that the best path to their implementation is to define cognitive processes (including those of a~moral nature) as consisting of information processing. What may help here may be the concept that such a~definition of moral cognition would not be a~naturalisation
%\label{ref:RNDAVNr8uUo2k}(Rosenbloom, 2015).
\parencite[][]{peruzzi_beginners_2015}. %
 This also could help to eliminate the troubling issue of the \textit{is-ought problem}. Although it is an issue considered by some theorists to be an illusory 
%\label{ref:RNDke81GSJMB7}(Gellner, 2005)
\parencite[][]{gellner_words_2005} %
 and an argument that is treated as untenable nowadays 
%\label{ref:RNDv1WxbP4FgK}(Searle, 1964)
\parencite[][]{searle_how_1964} %
 from point of view of ``weak'' rationality—as mentioned above.

@@

\paragraph{Acknowledgments.}
The author wishes to thank anonymous helpful referees whose insightful comments helped improve the quality of the present paper. Most certainly, if there are still some errors remaining, they are my own responsibility.
\enlargethispage{2\baselineskip}
